---
output: github_document
bibliography: inst/ref.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# erf-numerical-results

<!-- badges: start -->
<!-- badges: end -->

The goal of `erf-numerical-results` is to reproduce the results of the paper. 
For further details see @merg2020 [https://arxiv.org/abs/2201.12865]

## Dependencies
Make sure you install the packages listed in `main/dependencies.R`. In particular, you will need the `erf` package. To install it, run:

``` r
# install.packages("devtools")
devtools::install_github("nicolagnecco/erf")
```

## Clone repository
The repository works with `git lfs` [https://git-lfs.com/].
After you install `git lfs` on your system, you can clone the GitHub directory by
typing the following in your command line.

``` {r, engine = 'bash', eval=FALSE}
git lfs clone https://github.com/nicolagnecco/erf-numerical-results.git
```


## Reproduce figures
To create the figures in the paper, you can run `main/plots_for_manuscript.R`.

```{r eval=FALSE}
source("main/plots_for_manuscript.R")
```


## Run code
To run the code that produced the figures, you can run one of the individual files `main/sec_*.R`. Make sure to set the parameter `RUN_SIMULATION <- TRUE` at the top of the file you want to run.

**Note**: some simulations are computationally heavy, and run in parallel with 8--12 workers. To change the number of workers, specify `n_workers` in the file or its corresponding `configs/` file.

## References
